Kit Theory

### 2023-06-03 paper_old/paper.tex
Added new paper directory.

\usepackage{newunicodechar}
\newunicodechar{≡}{\ensuremath{\equiv}}
\newunicodechar{ℕ}{\ensuremath{\mathbb{N}}}
\newunicodechar{∘}{\ensuremath{\circ}}
\newunicodechar{∅}{\ensuremath{\varnothing}}
\newunicodechar{⇒}{\ensuremath{\Rightarrow}}
\newunicodechar{∋}{\ensuremath{\ni}}
\newunicodechar{∷}{\ensuremath{\mathop{::}}}
\newunicodechar{⊢}{\ensuremath{\vdash}}
\newunicodechar{∀}{\ensuremath{\forall}}
\newunicodechar{₁}{\ensuremath{{}_1}}
\newunicodechar{₂}{\ensuremath{{}_2}}
\newunicodechar{ᵣ}{\ensuremath{{}_{\textsf{r}}}}
\newunicodechar{ₛ}{\ensuremath{{}_{\textsf{s}}}}
\newunicodechar{→}{\ensuremath{\to}}
\newunicodechar{◆}{\ensuremath{\diamond}}
% \newunicodechar{Γ}{\ensuremath{\texttt{\Gamma}}}
% \newunicodechar{λ}{\ensuremath{\texttt{\lambda}}}

@@

    We propose a technique to derive the implementation and metatheory of
    renaming and substitution for all $m\cdot n$ combinations of variables and terms
    from a single term traversal and three simple lemmas for extrinsically typed
    but intrinsically scoped terms.
    We demonstrate the technique by formalizing type soundness of System F with
    very parallel substitutions, which replace both type and term variables at
    once, enabling a single substitution-preserves-typing lemma.
    We provide a well-documented implementation of the technique as an Agda
    library.

    Since the technique is based on extrinsic typing, the metatheory of renaming
    and substitution is decoupled from type preservation.
    This has the downside, that type preservation of renaming and substitution
    are not for free, but also the upside, that the library can be directly
    instantiated for object languages with non-standard typing relations like
    dependent types, type state, or resource environments.
  \end{abstract}

>>>>

\usepackage{bbold} % lower case mathbb letters

\usepackage{newunicodechar}
\newunicodechar{≡}{\ensuremath{\equiv}}
\newunicodechar{ℕ}{\ensuremath{\mathbb{N}}}
\newunicodechar{∘}{\ensuremath{\circ}}
\newunicodechar{∅}{\ensuremath{\varnothing}}
\newunicodechar{⇒}{\ensuremath{\Rightarrow}}
\newunicodechar{∋}{\ensuremath{\ni}}
\newunicodechar{∷}{\ensuremath{\mathop{::}}}
\newunicodechar{⊢}{\ensuremath{\vdash}}
\newunicodechar{∀}{\ensuremath{\forall}}
\newunicodechar{₁}{\ensuremath{{}_1}}
\newunicodechar{₂}{\ensuremath{{}_2}}
\newunicodechar{ᵣ}{\ensuremath{{}_{\textsf{r}}}}
\newunicodechar{ₛ}{\ensuremath{{}_{\textsf{s}}}}
\newunicodechar{→}{\ensuremath{\to}}
\newunicodechar{◆}{\ensuremath{\diamond}}
\newunicodechar{⊤}{\ensuremath{\top}}
\newunicodechar{★}{\ensuremath{\star}}
\newunicodechar{ˣ}{\ensuremath{{}^{\textsf{x}}}}
\newunicodechar{ᵅ}{\ensuremath{{}^{\textsf{\alpha}}}}
\newunicodechar{ᵥ}{\ensuremath{{}_{\textsf{v}}}}
\newunicodechar{ₜ}{\ensuremath{{}_{\textsf{t}}}}
\newunicodechar{𝕖}{\ensuremath{\mathbb{e}}}
\newunicodechar{𝕥}{\ensuremath{\mathbb{t}}}
\newunicodechar{𝕜}{\ensuremath{\mathbb{k}}}
\newunicodechar{∙}{\ensuremath{\bullet}}

% \newunicodechar{Γ}{\ensuremath{\texttt{\Gamma}}}
% \newunicodechar{λ}{\ensuremath{\texttt{\lambda}}}

@@

    We propose a technique to derive the implementation and metatheory of
    renaming and substitution for all $m\cdot n$ combinations of variables and terms
    from a single term traversal and three simple lemmas for extrinsically typed
    but intrinsically scoped terms.
    We demonstrate this technique by formalizing type soundness of System F with
    very parallel substitutions, which replace both type and term variables at
    once, enabling a single substitution-preserves-typing lemma.
    We provide a well-documented implementation of the technique as an Agda
    library.

    As the technique is based on extrinsic typing, the metatheory of renaming
    and substitution is decoupled from type preservation.
    This has the downside, that type preservation of renaming and substitution
    are not for free, but also the upside, that the library can be directly
    instantiated for object languages with non-standard typing relations like
    dependent types, type state, or resource environments.
  \end{abstract}
